
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Tushar}{Gautam}{ \urlstyle{same}\url{www.gtushar.in} \\
\href{mailto:tushar.rishav@gmail.com}{tushar[dot]rishav@gmail.com} | +91-9629931320
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection {\href{http://www.nitt.edu/}{NIT, Trichy, India}}
\descript{B.Tech, Production Engineering}
\location{Expected May 2017 | Trichy, TN, India \\ Cum. GPA: 7.52/10}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
GitHub:// \href{https://github.com/tushar-rishav}{\custombold{tushar-rishav}} \\
LinkedIn://  \href{https://www.linkedin.com/in/tusharrishav}{\custombold{tusharrishav}} \\
Quora:// \href{https://www.quora.com/profile/Tushar-50}{\custombold{Tushar-50}} \\
StackOverflow:// \href{http://stackoverflow.com/users/3673031/tushar-gautam}{\custombold{tushar-gautam}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework} 
\subsection{Undergraduate}
\textbullet{} Probability and Statistics (MA208)\\
\textbullet{} Image Processing (EC451)
\sectionsep
\subsection{Independent}
\textbullet{} Algorithms: Design and Analysis,\\ Stanford University,  Coursera\\
\textbullet{} Machine Learning, \\Stanford University, Coursera\\
\textbullet{} Website Performance Optimisation \\
\textbullet{} Introduction to Operating Systems
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Preferred:}
\textbullet{} Python \textbullet{} JavaScript \\
\location{Familiar:}
\textbullet{} C \textbullet{} C++ \textbullet{} CoffeeScript \textbullet{} Octave \\
\textbullet{} PHP  \textbullet{} SQL \\
\subsection{Technology}
\textbullet{} AngularJS \textbullet{} Flask \textbullet{} Node.js \\ \textbullet{} Git \textbullet{} Mocha/Chai \textbullet{} MongoDB \\
\textbullet{} Docker \textbullet{} GNU/Linux
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    POSITIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Positions} 
{\custombold{Core Member, Delta Force {\href{https://github.com/delta}{github.com/delta}} }}\\ 
The elite programming club of NIT, Trichy.
{\custombold{Maintainer, coala organisation {\href{https://github.com/coala}{github.com/coala}} }}\\ 
A language independent static code analyser.
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Hobbies} 
\textbullet{} Playing Cricket \\
\textbullet{} Traveling \\
\textbullet{} Watching TED talks \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\href{https://github.com/coala-analyzer/coala}{coala}}
\descript{\href{https://summerofcode.withgoogle.com/}{| Google Summer of Code Developer }}
\location{\href{https://www.python.org/psf/}{Python Software Foundation | April 2016 – August 2016 }}
\vspace{\topsep} 
\begin{tightemize}
\item Developed coala-html, a console app to generate an interactive webpage for static code analysis using coala. \textbf{\href{https://github.com/coala/coala-html}{\custombold{https://github.com/coala/coala-html} }} \end{tightemize}
\sectionsep

\runsubsection{\href{https://ep2016.europython.eu/conference/talks/guid-to-make-a-real-contribution-to-an-open-source-project-for-novice}{EuroPython}}
\descript{| Speaker }
\location{17 Jul 2016 – 24 Jul 2016 | Bilbao, Spain}
\vspace{\topsep} 
\begin{tightemize}
\item Conducted a training session titled \textbf{\href{https://ep2016.europython.eu/conference/talks/guid-to-make-a-real-contribution-to-an-open-source-project-for-novice}{"Guide to make an open source contribution"}}, using Git, Continuous Integration and Deployment tools. Participants made real time contributions to coala. (https://github.com/coala/coala)
\end{tightemize}
\sectionsep

\runsubsection{\href{http://www.citruspay.com/}{Citrus Payments}}
\descript{| Software Engineering Intern }
\location{May 2015 – Jul 2015 | Pune, India}
\vspace{\topsep} 
\begin{tightemize}
\item Refactored the existing JavaScript library to integrate a checkout page with Citrus payment gateway, resulting 40\% reduction in the codebase. \end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source PROJECTS}

\runsubsection{\href{https://github.com/coala/coala}{coala}}\\
\location{Contributor | Python}
A language independent static code analysis application. \textbf{\href{https://github.com/coala/coala}{\custombold{https://github.com/coala/coala} }}
\sectionsep

\runsubsection{\href{https://github.com/coala/coala-html}{coala-html}}\\
\location{Author | Python | AngularJS}
A console app to generate an interactive webpage for static code analysis using coala.
\textbf{\href{https://github.com/coala/coala-html}{\custombold{https://github.com/coala/coala-html} }}
\sectionsep

\runsubsection{\href{https://gitlab.com/gitmate/IGitt/}{IGitt}}\\
\location{Contributor | Python}
Unified interface to access various git hosting services like GitHub, GitLab etc.
\textbf{\href{https://gitlab.com/gitmate/IGitt/}{\custombold{https://gitlab.com/gitmate/IGitt/} }}
\sectionsep

\runsubsection{Code-Control}\\
\location{Contributor | NodeJS | MongoDB}
Code Character is a game for the players to code a character with attack and defend strategies and defeat the other players to win.
\textbf{\href{https://github.com/ash7594/code-control}{\custombold{https://github.com/ash7594/code-control}}}
\sectionsep

\runsubsection{Code2pdf}\\
\location{Author | Python}
Console app to convert a given source code into PDF file with the options for more than 20 syntax highlighting themes, custom PDF sizes and line formatting. \textbf{\href{https://github.com/tushar-rishav/code2pdf}{\custombold{https://github.com/tushar-rishav/code2pdf}}}
\sectionsep

\runsubsection{Balert}\\
\location{Author | Python}
A console app to generate voice notification when battery becomes low. User have the options to set custom warning messages, charge threshold and select English, Hindi or Tamil as one of the notification languages. \textbf{\href{https://github.com/tushar-rishav/balert}{\custombold{https://github.com/tushar-rishav/balert}}}
\sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}

