% !TEX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{mdframed}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tushar}{Gautam}{ \urlstyle{same}
\href{mailto:tushar.gautam@colorado.edu}{tushar.gautam@colorado.edu} | 720-421-2291 | \href{http://tushar-rishav.github.io/}{tushar-rishav.github.io}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Education} 

\subsection{University of Colorado Boulder}
\descript{MS, Computer Science | GPA: 4.0 \\ {\footnotesize \textit{\textbf{(focus on Intelligent Systems) }}}  }
\location{Expected, May 2023 | USA}
\sectionsep

\subsection{NIT Trichy}
\descript{B.Tech, Production Engineering}
\location{May 2017 | India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\textbullet{} Linkedin:// \href{https://www.linkedin.com/in/gautamtushar}{\underline {gautamtushar}} \\
\textbullet{} Github:// \href{https://github.com/tushar-rishav}{\underline {tushar-rishav}} \\
\textbullet{} Stackoverflow:// \href{https://stackoverflow.com/users/3673031/tushar-gautam}{\underline {tushar-gautam}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate
(Fall'21)}
\textbullet{} Design and Analysis of Algorithms \\
\textbullet{} Natural Language Processing \\
\textbullet{} Machine Learning
{\footnotesize \textit{\textbf{(Teaching Asst) }}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Programming Languages}
\textbullet{} JavaScript \\
\textbullet{} Python \\
\textbullet{} Rust  \\
\location{Technology and Platform}

\textbullet{} Ansible \\
\textbullet{} Ceph \\
\textbullet{} Docker \\
\textbullet{} Git \\
\textbullet{} Graylog \\
\textbullet{} HDFS \\
\textbullet{} HTML \\
\textbullet{} InfluxDB \\
\textbullet{} Kafka \\
\textbullet{} Kubeflow \\
\textbullet{} Kubernetes \\
\textbullet{} Linux \\
\textbullet{} Mesos \\
\textbullet{} MongoDB \\
\textbullet{} Nodejs \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{LG Ads}
\descript{| Software Engineer }
\location{June 2017 - June 2021 | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Optimised Automatic Content Recognition (ACR) service to add 5x improvement in search latency which significantly improved the granularity of the data available for business analytics.
\item Lead architect on key platform infrastructure projects which not only streamlined debugging, monitoring and deployment of the microservices but also significantly improved SLA for the customers. Tech stack involved: \textbf{Mesos}, \textbf{HDFS} and \textbf{Ceph} to maintain distributed storage and compute cluster, \textbf{Graylog} and \textbf{ElasticSearch} for log collection, \textbf{Telegraf} and \textbf{InfluxDB} for application metrics collection, \textbf{Docker} and \textbf{Kubernetes} for application deployment, \textbf{HaProxy} and \textbf{Floating IPs} for high-availability and load-balancing of the critical services.
\item Built \textbf{Machine Learning pipeline} using \textbf{Kubeflow} to save significant developer hours for the Data Science team.
\item Worked on building Automatic Speech Recognition for TV Operating System, evaluating and fine-tuning existing state-of-the-art pre-trained speech recognition models on internal dataset.
\end{tightemize}
\sectionsep

\runsubsection{Google}
\descript{| Google Summer of Code}
\location{April 2016 – August 2016}
\begin{tightemize}     
\item Contributed to Coala \textemdash static code analysis FOSS \textemdash in \textbf{Python}, under Python Software Foundation. Developed "coala-html" application \textemdash \textbf{AngularJS} application to display results from Coala, as an interactive web page.
\item Incorporated \textbf{test-driven development} with 97\%    \textbf{code coverage} for AngularJS and 100\% for Python codebase, \textbf{test automation} and wrote \textbf{code documentation} as recommended software development practices. \href{https://github.com/coala/coala-html}{https://github.com/coala/coala-html}.
\end{tightemize}
\sectionsep

\runsubsection{Europython}
\descript{| Speaker}
\location{July 2016 | Bilbao, Spain}
\begin{tightemize}
\item Presented a session on ”\textit{Guide to make an open source contribution}”, using \textbf{Git}, \textbf{CI/CD} pipeline at EuroPython — an annual International Python Conference in Europe. Participants made real time contributions to the Coala project. \href{https://tushar-rishav.github.io/EPGit/}{https://tushar-rishav.github.io/EPGit/}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Source Projects}
\textbullet{} \href{https://gitlab.com/gitmate/open-source/IGitt}{\underline {IGitt}} and \href{https://gitlab.com/gitmate/open-source/gitmate-2}{\underline {GitMate}} {\footnotesize \textit{\textbf{(Contributor, 2016) }}} \textemdash GitMate provides automated code review and issue triaging for GitHub projects. IGitt as a backbone for GitMate, provides REST interface to access git hosting services eg GitHub. Contributed bug fixes and implemented new feature to predict bug rank for incoming patch using bug prediction algorithm BugSpot from Google \\
\textbullet{} \href{https://github.com/ash7594/code-control/commits?author=tushar-rishav}{\underline {Code Control}} {\footnotesize \textit{\textbf{(Contributor, 2016) }}} \textemdash Online game based on Graph algorithms, player writes program in Javascript to control a bot character in 2D grid with attack and defend strategies and defeat opponent player’s character to win the game. Game was live during \href{Pragyan}{https://pragyan.org/21/home/} 2016 - annual Tech Fest at NIT Trichy
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
