%====================
% EXPERIENCE C
%====================
\subsection{{Senior Software Engineer - Anoki Inc \hfill  Mountain View, CA, USA  | June 2023 -- Current}}
\begin{zitemize}
\item Built \textbf{full-stack} contextual video search application, driving business revenues with AI-powered SSAI.
\item Implemented processing of 500+ concurrent live TV channel streams with \textbf{auto scale-out} capabilities.
\item Designed a \textbf{reliable ML pipeline} for deploying multi-modal vector search processing large-scale datasets spanning GPU cluster. 
\item Developed \textbf{recommendation system} for OTT application, enhanced user experience with hyper-personalization of TV channels.
\item Developed \textbf{core platform libraries} for Config Management and Service Discovery mechanisms based on Consul and Kubernetes.
\item Implemented GraphQL backends for Content Management \& Scheduling to on-board new content providers.
\item Managed infrastructure setup for \textbf{HAProxy} load balancers, \textbf{Presto} distributed SQL engine, \textbf{Superset} for data visualization, and \textbf{Consul} for application config.
\item Introductory discussions with team on best development practices.
\end{zitemize}
\textit{Skills}: Go, Python, TypeScript, Svelte/SvelteKit, Kubernetes, Metaflow, Airflow, Protobuf, gRPC, MySQL, MongoDB, Consul, Presto, Superset, HaProxy, GraphQL, Prometheus, Grafana and AWS - Mediaconvert, S3, Cloudfront, RDS, EKS.
\vspace*{2mm}
\subsection{{Software Engineer Intern - PayPal \hfill New York City, NY, USA | May 2022 -- August 2022}}
\begin{zitemize}
\item Added static type safety for GraphQL resolvers based on a schema-first design philosophy, increasing code maintainability.
\end{zitemize}

\textit{Skills}: TypeScript, GraphQL.
\vspace*{1mm}

%====================
% EXPERIENCE B
%====================
\subsection{{Software Engineer - LG Ads \hfill Bangalore, KA, India | June 2017 --- June 2021}}
\begin{zitemize}
\item 5x latency optimization for a large-scale fingerprint distribution network for Audio Content Recognition system.
\item Lead projects in the realm of core platform development with monitoring, logging and distributed storage infrastructure. 
\item Setup and managed key infrastructure projects: load balancers, and large-scale Spark cluster.
\end{zitemize}

\textit{Skills}: NodeJS, Python, Airflow, Bash, Docker, MySQL, HDFS, Ceph, Spark, Mesos, Kafka, Ansible, Jenkins, Prometheus, EtcD, HAProxy, Linux firewall.
\vspace*{1mm}

\subsection{{Google Summer of Code - Python Software Foundation \hfill Bangalore, KA, India | April 2016 -- August 2016}}
\begin{zitemize}
\item Built interactive static code analysis tool with 97\% code coverage for frontend and, 100\% for backend.
\item Presented a workshop on \textit{"Guide to open-source contributions using Git and CI/CD"} at EuroPython conference in Bilbao, Spain.
\end{zitemize}
\textit{Skills}: Python, AngularJS, HTML, CSS, Git, TravisCI, Docker, Karma, Mocha, ChaiJS, Test Driven Development.
